Type Classes for Mathematics in Type Theory

### 2010-06-28 jar.tex
Add paragraph about opacity and unpredictability of instance resolution.

\lstinline|Decision| is a very general purpose type class that also works for predicates. For instance, to declare a parameter expressing decidability of, say, (setoid) equality on a type \lstinline|X|, we write: \lstinline|`{Π a b: X, Decision (a = b)}|. To then use this (unnamed) decider to decide a particular equality, we simply say \lstinline|decide (x = y)|, and instance resolution will resolve the decider we declared.

@@

>>>>

\lstinline|Decision| is a very general-purpose type class that also works for predicates. For instance, to declare a parameter expressing decidability of, say, (setoid) equality on a type \lstinline|X|, we write: \lstinline|`{Π a b: X, Decision (a = b)}|. To then use this (unnamed) decider to decide a particular equality, we simply say \lstinline|decide (x = y)|, and instance resolution will resolve the decider we declared.

@@

Because predicate classes only provide contextual information and are insulated from the actual algebraic expressions, their instances can always be kept entirely opaque---only their existence matters. Together, these properties largely defuse an argument occasionally voiced against type classes concerning perceived unpredictability of instance resolution. While it is certainly true that in contexts with redundant information it can become hard to predict which instance of a predicate class will be found by proof search, this is simply a non-issue because it \emph{does not matter} which one is found.
